L'Identification des Projets de Logiciel Libre Accessibles aux Nouveaux Contributeurs

### 2022-12-16 EIAH_2023_paper/paper.tex
EIAH: improve abstracts' keywords

% language settings
\usepackage[main=french,english]{babel}
\newcommand{\en}[1]{\foreignlanguage{english}{\emph{#1}}}
\usepackage{csquotes}
\MakeOuterQuote{"}

@@

        \todo{TODO : utiliser comme mots-clé les catégories de la conférence (pour les deux ou trois
        premiers)}
        \textbf{Mots-clé :} Logiciel libre, Analyse automatique de dépôts logiciels, Barrières d'entrée du
        logiciel libre, Nouveaux contributeurs.
    \end{abstract}
    \selectlanguage{english}
    \begin{abstract}
        FOSS makes an increasing amount of the public and industrial software landscape, notably for its
        transparency and democratic governance. However, simply publishing the source code of a software does
        not automatically make it accessible, and many barriers impede new contributors approaching these
        projects. Through a large-scale software mining of the Software Heritage archive, we test the
        pertinence of three signals in the identification of accessible FOSS projects for new contributors.
        Our results show a positive correlation between the number of new contributors of a project
        successfully bringing their contribution to completion and the presence of contributing guidelines, as
        well as between that same number and the number of recent unique contributors in the project. Such
        signals could find a use in the teaching of FOSS practices, as teachers of this subject often find it
        difficult to select an accessible project for their students to work on.

        \textbf{Keywords:} FOSS, Mining Software Repositories, Open source barriers to entry, New
        contributors.
    \end{abstract}
    \selectlanguage{french}

>>>>

% language settings
\usepackage[main=french,english]{babel}
\newcommand{\en}[1]{\foreignlanguage{english}{\emph{#1}}}
\usepackage{csquotes}
\MakeOuterQuote{"}
% Fix LLNCS language handling of the "keywords" part of the abstracts
\addto{\captionsfrench}{\renewcommand{\keywordname}{\textbf{Mots-clé:}}}

@@

        \keywords{
            Collecte, traitement et analyse des traces d’apprentissage \and
            Analyse d’usage(s) et de pratiques \and
            Logiciel libre \and
            Analyse automatique de dépôts logiciels \and
            Barrières d'entrée du logiciel libre
        }
    \end{abstract}
    \selectlanguage{english}
    \begin{abstract}
        FOSS makes an increasing amount of the public and industrial software landscape, notably for its
        transparency and democratic governance. However, simply publishing the source code of a software does
        not automatically make it accessible, and many barriers impede new contributors approaching these
        projects. Through a large-scale software mining of the Software Heritage archive, we test the
        pertinence of three signals in the identification of accessible FOSS projects for new contributors.
        Our results show a positive correlation between the number of new contributors of a project
        successfully bringing their contribution to completion and the presence of contributing guidelines, as
        well as between that same number and the number of recent unique contributors in the project. Such
        signals could find a use in the teaching of FOSS practices, as teachers of this subject often find it
        difficult to select an accessible project for their students to work on.

        \keywords{
            Collection, processing and analysis of learning traces \and
            Usage and practices analysis \and
            FOSS \and
            Mining Software Repositories \and
            Open source barriers to entry
        }
    \end{abstract}
    \selectlanguage{french}
